Kindly Bent to Free Us

### 2019-11-23 kindly/sdtyping/extra.tex
Move explanation of Let in the appendix.
Added typing for internal language.
Make sure splitting rules are all the same.
Added typing for internal language in A-normal form.
Partially fixed layout of appendix.

\subsection{Kinding}
%
\begin{figure}[bt]
  \centering
  \input{sdtyping/sd-kinds}
  \caption{Syntax-directed kinding rule --
    $\inferSK{C}{\E}{\tau}{k}$}
  \label{rules:sd-kinding}
\end{figure}

@@

\begin{figure*}[!tb]
  \input{sdtyping/sd-splitting}
  \caption{Splitting ---
    environments $\lsplit C\E{\E_l}{\E_r}$;
    inference $\bsplit C\E{\inP{\E_l}}{\inP{\E_r}}$;
    binders $\bsplit Cb{\inP{b_r}}{\inP{b_l}}$}
  \label{fig:sd-splitting}
  \input{sdtyping/sd-borrowing}
  \caption{Borrowing ---
    environments $\lregion[n]{C}{x}{\E}{\E'}$;
    inference $\bregion[\inP n]{C}{\inP x}{\E}{\inP{\E'}}$;
    binders $\bregion[\inP n]{C}{\inP x}{b}{\inP{b'}}$}
  \label{fig:sd-borrowing}
  \input{sdtyping/sd-environments}
  \caption{Rewriting constraints on environments --- $\inP{\Cleq{\E}{k}}\Crewrite  C$}
  \label{fig:contraints-environments-types}
\end{figure*}

@@

The rules for syntax-directed typing are shown in \cref{fig:syntax-directed-typing}
and follow the presentation given in \cref{sdtyping}.
As usual in HM type systems, introduction of type-schemes
is included in the {\sc Let} rule via generalization.
We define $\generalize{C}{\E}{\tau} =
(\Cproj{\Multi{\kvar},\Multi{\tvar}}{C},
\forall \Multi{\kvar},\Multi{\tvar}.\qual{C}{\tau})$
where
$\Multi{\kvar},\Multi{\tvar} = (\fv{\tau}\cup\fv{C})\setminus\fv{\E}$.

\begin{figure*}[hbtp]
  \input{sdtyping/sd-typing}
  \caption{Syntax-directed typing rules --
    $\inferS{C}{\E}{e}{\tau}$}
  \label{fig:syntax-directed-typing}
\end{figure*}

>>>>

\begin{figure}[bt]
  \centering
  \input{sdtyping/sd-kinds}
  \caption{Syntax-directed kinding rule --
    $\inferSK{C}{\E}{\tau}{k}$}
  \label{rules:sd-kinding}
\end{figure}

\begin{figure}[!tbp]
  \input{sdtyping/sd-splitting}
  \caption{Splitting ---
    environments $\lsplit C\E{\E_l}{\E_r}$;
    inference $\bsplit C\E{\inP{\E_l}}{\inP{\E_r}}$;
    binders $\bsplit Cb{\inP{b_r}}{\inP{b_l}}$}
  \label{fig:sd-splitting}
\end{figure}
\begin{figure*}[!tbp]
  \input{sdtyping/sd-borrowing}
  \caption{Borrowing ---
    environments $\lregion[n]{C}{x}{\E}{\E'}$;
    inference $\bregion[\inP n]{C}{\inP x}{\E}{\inP{\E'}}$;
    binders $\bregion[\inP n]{C}{\inP x}{b}{\inP{b'}}$}
  \label{fig:sd-borrowing}
\end{figure*}
\begin{figure*}[!tbp]
  \input{sdtyping/sd-environments}
  \caption{Rewriting constraints on environments --- $\inP{\Cleq{\E}{k}}\Crewrite  C$}
  \label{fig:contraints-environments-types}
\end{figure*}
\begin{figure*}[!tbp]
  \input{sdtyping/sd-typing}
  \caption{Syntax-directed typing rules --
    $\inferS{C}{\E}{e}{\tau}$}
  \label{fig:syntax-directed-typing}
\end{figure*}
\begin{figure*}[!btp]
  \input{sdtyping/sd-typing-internal}
  \caption{Syntax-directed typing rules for internal language --
    $\inferS{C}{\E}{e}{\tau}$}
  \label{fig:syntax-directed-typing-internal}
\end{figure*}
\begin{figure*}[!btp]
  \input{sdtyping/sd-typing-internal-a}
  \caption{Syntax-directed typing rules for internal language in A-normal form --
    $\inferS{C}{\E}{e}{\tau}$}
  \label{fig:syntax-directed-typing-internal-a}
\end{figure*}

\subsection{Kinding}

@@

@@

The rules for syntax-directed typing are shown in \cref{fig:syntax-directed-typing}
and follow the presentation given in \cref{sdtyping}.
As usual in HM type systems, introduction of type-schemes
is included in the {\sc Let} rule via generalization.
We define $\generalize{C}{\E}{\tau} =
(\Cproj{\Multi{\kvar},\Multi{\tvar}}{C},
\forall \Multi{\kvar},\Multi{\tvar}.\qual{C}{\tau})$
where
$\Multi{\kvar},\Multi{\tvar} = (\fv{\tau}\cup\fv{C})\setminus\fv{\E}$.
The typing rules specific to the internal language are shown in
\cref{fig:syntax-directed-typing-internal}.
The typing rules specific to the internal language in A-normal form are shown in
\cref{fig:syntax-directed-typing-internal-a}.
